\documentclass[a4paper,12pt]{article}
%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	
%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}
%tabularx environment
\usepackage{tabularx}
%for lists within experience section
\usepackage{enumitem}
% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 
%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}
%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}
%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}
%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}
%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}
%for social icons
\usepackage{fontawesome5}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=1mm,noitemsep]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{2mm}}

\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=3ex, rightmargin=2ex, noitemsep,labelsep=1.2mm,itemsep=0mm]\small}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2mm}}


\newcommand{\resumeSubheading}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#4}}\\
        \textit{\footnotesize{#3}} &  \footnotesize{#2}
    \end{tabular*}
}

\newcommand{\resumeExperience}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#3}}\\
        \textit{\footnotesize{#2}} & {}
    \end{tabular*}\\ [1mm]
    \footnotesize{#4}
}

\newcommand{\resumeProject}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#3}} \\
        \footnotesize{\textit{#2}} & \footnotesize{#4}
    \end{tabular*}
}
\newcommand{\emptyLine}{\\[-3mm]}

%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}
% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Deepu K B} \\[7.5pt]
\href{https://github.com/deepu-kb}{GitHub: github.com/deepu-kb} \ $|$ \ 
\href{https://www.linkedin.com/in/deepu-k-b-05a152184/}{LinkedIn: linkedin.com/in/deepu-k-b-05a152184} \ $|$ \ 
\href{mailto:k.bdeepu40@gmail.com}{Email: k.bdeepu40@gmail.com} \ $|$ \ 
\href{tel:+917353788441}{Phone: +91-7353788441} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------

%Interests/ Keywords/ Summary
\section{Summary}
\textbf{.NET Full Stack Developer} with \textbf{4+ years of experience} designing, developing, and maintaining scalable web applications using C\#, ASP.NET Core, .NET Framework, Entity Framework Core, LINQ, REST APIs, MS SQL Server, JavaScript, ReactJS, Umbraco CMS, Squidex, and Microsoft Azure. Experienced in building CMS-driven websites, modernizing legacy systems, migrating WCF services to .NET Core Web API, developing reports and dashboards, and supporting CI/CD deployments using TeamCity, Octopus Deploy, and IIS. Strong knowledge of SDLC, Object-Oriented Programming (OOP), database design, performance optimization, debugging, and production support with a track record of delivering maintainable enterprise solutions.

%Education
\section{\textbf{Education}}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Malnad College Of Engineering,Hassan}{CGPA: 8.72}
      {Bachelor of Engineering (Information Science and Engineering)}{2017 - 2021}
    \resumeSubheading
      {Sri Venkateshwara P U College, Hassan}{Percentage: 85.66}
      {Pre-University Course (Science) }{2017}
    \resumeSubheading
      {Sri Aravinda High School, Hassan}{Percentage: 88.64}
      {Class 10th}{2015}
  \resumeSubHeadingListEnd

%-----------Technical skills-----------------
\section{\textbf{Technical Skills}}
 \begin{itemize}[leftmargin=0.1in, label={}]
    \small{\item{
     \textbf{Languages}{: C\#, SQL, HTML, CSS, JavaScript} \\
     \textbf{Frameworks/Libraries}{: ASP.NET Core, .NET Framework, .NET Core Web API, Entity Framework Core, LINQ, ReactJS} \\
     \textbf{CMS \& Web Platforms}{: Umbraco CMS, Squidex, CMS-driven websites} \\
     \textbf{Developer Tools}{: Visual Studio, VS Code, Git, GitHub} \\
     \textbf{Databases}{: MS SQL Server, Oracle, MongoDB} \\
     \textbf{APIs \& Protocols}{: REST APIs, Web API} \\
     \textbf{Cloud}{: Microsoft Azure} \\
     \textbf{CI/CD \& Deployment}{: TeamCity, Octopus Deploy, IIS} \\
     \textbf{Other Skills}{: Data Structures \& Algorithms, SDLC, Object-Oriented Programming (OOP), Debugging, Performance Optimization} \\
     \textbf{Soft Skills}{: Problem Solving, Communication, Teamwork, Adaptability, Time Management} \\
    }}
 \end{itemize}

%Experience
\section{Work Experience}

\resumeSubHeadingListStart
\resumeExperience {HCL Technologies Limited}
 {Lead Engineer} {Feb 2025 - Current}
 {\textbf{Client:} BBC Studios}
 
 \resumeItemListStart
  \item Developed and maintained CMS-driven websites and digital platforms for BBC Studios using Umbraco CMS, Squidex, ASP.NET Core, C\#, REST APIs, and Microsoft Azure.
  \item Built reusable components, templates, and backend integrations to improve content publishing workflows, website performance, and user experience.
  \item Delivered responsive, maintainable, and production-ready features in collaboration with business stakeholders, designers, QA engineers, and release teams.
  \item Supported CI/CD pipelines using TeamCity and Octopus Deploy for automated builds, deployments, release validation, and troubleshooting.
  \item Participated in requirement analysis, technical design discussions, code reviews, defect resolution, and release management for enterprise web applications.
 \resumeItemListEnd

 \vspace{4mm}
 \textbf{Key Projects:}
 \resumeItemListStart
       \item BBC Studios Digital Creative: Website for digital content management and delivery.
       \item BBC Polska: Website.
       \item BBC Africa Channels -- Hidden Gems Campaign: Website for BBC Africa campaign content.
 \resumeItemListEnd

 \resumeSubHeadingListEnd

 \resumeSubHeadingListStart
 \resumeExperience {Surya Financial Technologies Private Limited}
  {Software Development Engineer - II} {Jun 2022 - Feb 2025}
  {}

 \resumeItemListStart
   \item Designed, developed, and maintained enterprise web applications using C\#, ASP.NET Core, .NET Framework, REST APIs, and MS SQL Server.
   \item Migrated services from WCF to .NET Core Web API, improving system performance by 40\% and enhancing scalability and maintainability.
   \item Gathered client requirements and translated business needs into technical specifications, development tasks, and implementation plans.
   \item Developed dynamic web forms, validations, backend services, and database queries to support accurate and user-friendly data processing.
   \item Built analytics reports and dashboards for data visualization, enabling stakeholders to review financial and risk insights.
   \item Executed data migration and ETL activities with focus on data integrity, validation, and smooth transition between systems.
   \item Deployed and supported applications on IIS in production environments, including configuration, issue analysis, and release troubleshooting.
   \item Reviewed code and guided junior developers on coding standards, debugging practices, and project workflows.
 \resumeItemListEnd

 \vspace{4mm}
 \textbf{Key Projects:}
 \resumeItemListStart
       \item PFS (Planning and Forecasting System): Developed a report-based financial forecasting system using .NET Core and MS SQL, enabling streamlined data handling and accurate forecasting results.
       \item IRRBB (Interest Rate Risk in the Banking Book): Built a report-based dashboard for real-time risk aggregation and analytics, allowing enhanced visibility and assessment of interest rate risks.
       \item Risk Aggregator: Designed and implemented a solution for consolidating risk data from multiple financial sources, significantly improving data accuracy and enabling comprehensive risk analysis.
 \resumeItemListEnd

 \resumeSubHeadingListEnd

 \resumeSubHeadingListStart
 \resumeExperience {Surya Software Systems Private Limited}
  {Software Development Engineer - I} {Aug 2021 - May 2022}
  {}

 \resumeItemListStart
   \item Developed and maintained web application modules using ASP.NET, C\#, .NET Core, SQL, HTML, JavaScript, and REST API concepts.
   \item Fixed defects, optimized code, and improved application reliability, performance, and maintainability.
   \item Implemented backend services, frontend components, and dynamic web forms under guidance from senior developers and project leads.
   \item Participated in requirement analysis and converted business requirements into technical tasks and deliverables.
   \item Supported deployment activities, configuration changes, release troubleshooting, and post-release issue resolution.
   \item Collaborated with cross-functional teams to maintain existing applications and deliver enhancements within project timelines.
 \resumeItemListEnd

 \vspace{4mm}
 \textbf{Key Projects:} 
 \resumeItemListStart
       \item BASEL: Assisted in improving the performance and compliance of the BASEL application by supporting risk assessment features and ensuring regulatory adherence.
       \item PFS (Planning and Forecasting System): Contributed to the development of this report-based forecasting system, optimizing data input forms and user interactions to streamline data entry processes.
 \resumeItemListEnd
 \resumeSubHeadingListEnd


 \vfill
 % \center{\footnotesize Last updated: \today}

 \end{document}
